A Large-scale Study of Polymorphism in R

### 2019-03-18 paper/main.tex
minor

The first distinction that can be made is based on the value of the
\code{typeof} function.  This function, given a value, will return one of
the following types: \code{logical} (vector of booleans), \code{integer}
(vector of integers), \code{double} (vector of floating points),
\code{complex} (vector of complex numbers), \code{character} (vector of
character strings), \code{raw} (vector of bytes) and \code{list}
(polymorphic vector), \x`code{NULL} (vector of NULL),
\code{closure} (function), \code{environment} (naming environment),
\code{S4} (S4 object) and others that are used within the implementation of
R (\code{special}, \code{builtin}, \code{symbol}, \code{pairlist},
\code{promise}, \code{language}, \code{char}, \code{...}, \code{any},
\code{expression}, \code{externalptr}, \code{bytecode} and \code{weakref}).

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bib/biblio,bib/jv,bib/r,bib/new}

>>>>

The first distinction that can be made is based on the value of the
\code{typeof} function.  This function, given a value, will return one of
the following types: \code{logical} (vector of booleans), \code{integer}
(vector of integers), \code{double} (vector of floating points),
\code{complex} (vector of complex numbers), \code{character} (vector of
character strings), \code{raw} (vector of bytes) and \code{list}
(polymorphic vector), \code{NULL} (vector of NULL),
\code{closure} (function), \code{environment} (naming environment),
\code{S4} (S4 object) and others that are used within the implementation of
R (\code{special}, \code{builtin}, \code{symbol}, \code{pairlist},
\code{promise}, \code{language}, \code{char}, \code{...}, \code{any},
\code{expression}, \code{externalptr}, \code{bytecode} and \code{weakref}).

@@

\bibliographystyle{boilerplate/ACM-Reference-Format}
\bibliography{bib/biblio,bib/jv,bib/r,bib/new}
